SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-06 scipy-1.0/paper.tex
Added C language family section to language choices description along with appropriate references.

>>>>

Rounding out the top three languages in SciPy is C, which is also extremely
well-established over several decades\cite{Kernighan:1988:CPL:576122} of
scientific computing. Alongside its objected-oriented relative C++, C
can be leveraged in Python after being exposed using the Cython
language. Cython has been described as a creole language that mixes
the best parts of Python and lower-level C / C++
paradigms\cite{behnel2011cython}. We thus often use Cython as a glue
between well-established low-level scientific computing libraries and
the Python interface offered by SciPy. We also use Cython to enable
performance enhancements in Python code, especially for cases where heavily
used inner loops benefit from a compiled code with static typing. Some of the C
libraries that we wrap in SciPy include trlib\cite{doi:10.1080/10556788.2018.1449842} 
(iterative solving of the trust region problem), SuperLU\cite{li05,superlu_ug99} (solution of
large, sparse, nonsymmetric systems of linear equations),
Qhull\cite{Barber:1996:QAC:235815.235821} (computational
geometry), and Cephes\cite{cephes_netlib} (mathematics algorithms).
